Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
line breaks

By combining and applying state-of-the-art synthesis engines we present a 
tool that automatically generates digital controllers for a given 
continuous plant model that are correct by construction.  
This approach presents a high degree of autonomy, 
promises to reduce the cost and time of development of digital control dramatically, 
and requires considerably less expertise than a-posteriori verification methodologies.   
Specifically, we synthesize stable,  
%controllers for hybrid closed-loop systems, i.e., 
software-implemented embedded controllers along with a model of a physical plant. 
%, that are \emph{stable}.  
Due to the complexity of such closed-loop systems, in this work we focus
on linear models with known configurations, and perform parametric synthesis
of stabilizing digital controllers (further closed-loop requirements are left to future work).

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  
Towards our goal of closed-loop stability, 
% despite digitization effects, 
we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
discretization. 
% elements with quantization noise.  
%
We further account for uncertainties on the plant models.  The resulting
closed-loop system is a program loop that operates on bit-vectors encoded
using fixed-point arithmetic with finite word length (FWL).  The three
effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization
errors are incorporated into the model,
%
%as an additive uncertainty, 
and are taken into account during the CEGIS-based synthesis of the control software for the plant.

@@

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system (cf. Section \ref{verifying-closed-loop-control-systems} for notations) \label{fig:sampledsystem}}
\end{figure*}

>>>>

By combining and applying state-of-the-art synthesis engines we present a
tool that automatically generates digital controllers for a given continuous
plant model that are correct by construction.  This approach presents a high
degree of autonomy, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification methodologies.  Specifically, we synthesize
stable, software-implemented embedded controllers along with a model of a
physical plant.  Due to the complexity of such closed-loop systems, in this
work we focus on linear models with known configurations, and perform
parametric synthesis of stabilizing digital controllers (further closed-loop
requirements are left to future work).

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  Towards our goal of closed-loop stability, we have modeled
a digital equivalent of the continuous plant by evaluating the effects of
the quantizers (A/D and D/A converters) and of time discretization.  We
further account for uncertainties on the plant models.  The resulting
closed-loop system is a program loop that operates on bit-vectors encoded
using fixed-point arithmetic with finite word length (FWL).  The three
effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization errors
are incorporated into the model, and are taken into account during the
CEGIS-based synthesis of the control software for the plant.

@@

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system (cf.~Section \ref{verifying-closed-loop-control-systems} for notation) \label{fig:sampledsystem}}
\end{figure*}
